---
title: "Forte Hotel Design"
author: "Krishanthi Weragalaarachchi"
date: "7/20/2021"
output: html_document
params: 
  Name: "Krishanthi Weragalaarachchi"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
your_name <- readline(prompt = "What is your name?      ")
```

```{r}
print(your_name)
print(params$Name)
```
```{r}
date()
```
I have a mac and following code was run to get the IP address

```{r}
x <- system("ifconfig", intern=TRUE)
z <- x[grep("\tinet", x)]
gsub(".*? ([:digit:])", "\\1", z[5])

```
## Data Setup

installing libraries, set the directory and read the data
```{r results='hide', message=FALSE, warning=FALSE}
library(cluster)
library(conjoint)
library(dplyr)
library(fpc)  
library(broom) 
library(ggplot2)
library(tidyverse)
```

```{r}
setwd("/Users/krishanthi/Documents/KSU/MANGT880/Project")
bundles_data <- read.csv("bundles.csv")
design_data <-  read.csv("design.csv")
ratings_data <- read.csv("ratings.csv")
existing_prof_data <- read.csv("existing_profiles.csv")
new_prof_data <- read.csv("new_profiles.csv")
```
remove attributes column from each dataset
```{r}
design <- design_data[,-1]
design
ratings <- ratings_data[,-1]
head(ratings)
bundles <- data.frame(bundles_data[,-1])
existing <- data.frame(existing_prof_data[,-1])
new <- data.frame(new_prof_data[,-1])

```
making of data sets with codes
```{r}
replace_1 <- c("Small_Suite","Internet_access","Exercise_room","Shoe_shine","Yes")
replace_2 <- c("Large_Room" ,"No", "Pool" ,"Speaker_phone" ,"Tape_library")
replace_3 <- c("Exercise_room_and_Pool", "Fruit_and_cheese", "Room_fax", "Room_Office")
replace_4 <- c("Newspaper")

bundles <- as.data.frame(sapply(bundles, function(x) 
  gsub(paste0(replace_3, collapse = '|'), 3, x)))
bundles <- as.data.frame(sapply(bundles, function(x) 
  gsub(paste0(replace_1, collapse = '|'), 1, x)))
bundles <- as.data.frame(sapply(bundles, function(x) 
  gsub(paste0(replace_2, collapse = '|'), 2, x)))
bundles <- as.data.frame(sapply(bundles, function(x) 
  gsub(paste0(replace_4, collapse = '|'), 4, x)))
bundles <- data.frame(t(bundles))
bundles <- bundles %>% rename("Room" = X1, "Bus_Amenities" = X2, "Leisure" = X3, "Extras" =X4, "Rest_Delivery" =X5)
row.names(bundles) <-NULL
bundles

existing <- as.data.frame(sapply(existing, function(x) 
  gsub(paste0(replace_3, collapse = '|'), 3, x)))
existing <- as.data.frame(sapply(existing, function(x) 
  gsub(paste0(replace_1, collapse = '|'), 1, x)))
existing <- as.data.frame(sapply(existing, function(x) 
  gsub(paste0(replace_2, collapse = '|'), 2, x)))
existing <- as.data.frame(sapply(existing, function(x) 
  gsub(paste0(replace_4, collapse = '|'), 4, x)))
existing <- data.frame(t(existing))
existing <- existing %>% rename("Room" = X1, "Bus_Amenities" = X2, "Leisure" = X3, "Extras" =X4, "Rest_Delivery" =X5)
row.names(existing) <-NULL
existing

new <- as.data.frame(sapply(new, function(x) 
  gsub(paste0(replace_3, collapse = '|'), 3, x)))
new <- as.data.frame(sapply(new, function(x) 
  gsub(paste0(replace_1, collapse = '|'), 1, x)))
new <- as.data.frame(sapply(new, function(x) 
  gsub(paste0(replace_2, collapse = '|'), 2, x)))
new <- as.data.frame(sapply(new, function(x) 
  gsub(paste0(replace_4, collapse = '|'), 4, x)))
new <- data.frame(t(new))
new <- new %>% rename("Room" = X1, "Bus_Amenities" = X2, "Leisure" = X3, "Extras" =X4, "Rest_Delivery" =X5)
row.names(new) <-NULL
new
```

levelnames dataframe
```{r}
levelnames <-data.frame(levels=c("Small_Suite", "Large_Room", "Room_Office",
                                 "Internet_access","Speaker_phone","Room_fax", 
                                 "Exercise_room","Pool", "Exercise_room_and_Pool",
                                 "Shoe_shine", "Tape_library","Fruit_and_cheese","Newspaper",
                                 "Yes", "No"))

```
## Conjoit Analysis

Measurement of part-worths utilities (all respondents): 
```{r}
part_utilities=caPartUtilities(y=ratings,x=bundles,z=levelnames) 
print(head(part_utilities))
#write.csv(part_utilities,"part_utilities_all_respondents.csv")
```
levelnames of maximum part_utilities for each respondent
```{r}
colnames(part_utilities[,-1])[max.col(part_utilities[,-1])]
```
Measurement of total utilities (all respondents):
```{r}
total_utilities=caTotalUtilities(y=ratings,x=bundles) 
print(head(total_utilities)) 
# write.csv(total_utilities,"total_utilities_all_respondents.csv")
```
Frequency of bundle choice 
```{r}
bundle_names <-unlist(apply(total_utilities, 1, function(x) which(x == max(x)))) # bundle choice for each respondent
Bundle_choice <- data.frame(table(bundle_names)) # buying frequency for each bundle
#write.csv(Bundle_choice,"choices_for_16bundles.csv")
Bundle_choice

```

importance of attributes (considering all respondents)
```{r}
importance_all=caImportance(y=ratings,x=bundles) 
print(importance_all)
```
analysis and graphs from Conjoint function for all respondents

###impoartant: 
In mac, qurtz opens up for bitmap image rendering for Conjoint(). Then later causes trouble opening plot preview for other plots for some reason. Aslo this causes R to stop when knitting to HTML. I did not have time to figure out a way to avoid that. Only happens in Rmarkdown. all plots generated using R are included in the report.
```{r}
#Conjoint(y=ratings,x=bundles,z=levelnames)

```
Beta coefficients or partwoth utility from the model for all respondents
```{r}
partworth_all <- data.frame('intercept' = 43.69, "Small_Suite"=3,"Large_Room"= -3.2438,
                                  "Room_Office" = 0.2438, "Internet_access" = -1.4687, 
                                  "Speaker_phone"=0.9063, "Room_fax"=0.5625,"Exercise_room"=-0.9979,
                                  "Pool"=0.3896,"Exercise_room_and_Pool"=0.6083,"Shoe_shine"=0.1047,
                                  "Tape_library"=-1.2641,"Fruit_and_cheese"=0.8859,"Newspaper"=0.2734,
                                  "Yes"=0.0078,"No"=-0.0078)
partworth_all
```

function to calculate preferance-share for each respondent
```{r}
Preference_share <- function(partworths,simulations) {
  for (j in seq(1:length(colnames(simulations[,-1])))) {
    mylist<- c()
    for (i in seq(1:length(colnames(partworths)))) {
      coln <- colnames(partworths)[i]
      if (coln %in% simulations[,j] || coln == "intercept"){
        mylist<- c(mylist,coln)
        pat <- quo_name(enquo(j))
        newN <- paste0(pat, "_sum")
        newPref <-partworths %>%
          select(all_of(mylist)) %>% 
          reduce(`+`) 
        partworths<-partworths %>%
          mutate(!!newN := newPref)
      }
    }
  }
  new_preferances<-partworths[,17:ncol(partworths)]
  return( new_preferances)
}
```

```{r}
Preference_share(partworth_all,bundles_data[,-1])
```

the relative importance of features (for the respondent named Nissa):
```{r}
importance_nissa=caImportance(y=ratings[26,],x=bundles) 
print(importance_nissa)
```
analysis and graphs from Conjoint function for respondent Nissa

###impoartant: 
In mac, qurtz opens up for bitmap image rendering for Conjoint(). Then later causes trouble opening plot preview for other plots for some reason. Aslo this causes R to stop when knitting to HTML. I did not have time to figure out a way to avoid that. Only happens in Rmarkdown. all plots generated using R are included in the report.
```{r}
#Conjoint(ratings[26,],bundles,levelnames) 
```

## Segmentation Analysis

Segmentation using k-means method - the default division into 2 segments:
```{r}
segments<-caSegmentation(ratings,bundles) 
print(segments$seg) 
```
center menas and overall means
```{r}
center_means<-as.data.frame(t(segments$seg$centers)) # center menas
means <-as.data.frame(apply(ratings, 2, mean)) # overall means
segment_ana <- cbind(center_means,means)
segment_ana<-segment_ana %>% rename("cluster_1" = "1", "cluster_2"="2", "overall_mean" = "apply(ratings, 2, mean)")
segment_ana
#write.csv(segment_ana,"cluster_means.csv")
```
adding members 
```{r}
members<-data.frame(respondent=ratings_data[,1],segment=as.numeric(strsplit(as.character(segments$seg$cluster)," ")))
members
```
conjoint analysis for clusters 1 

###impoartant: 
In mac, qurtz opens up for bitmap image rendering for Conjoint(). Then later causes trouble opening plot preview for other plots for some reason. Aslo this causes R to stop when knitting to HTML. I did not have time to figure out a way to avoid that. Only happens in Rmarkdown. all plots generated using R are included in the report.
```{r}
clusters <- cbind(ratings,members[,2])
clusters <- clusters %>% rename("segment"="members[, 2]")
cluster1 <- clusters[clusters[,"segment"] == 1,] # respondents in cluster 1
#Conjoint(y=cluster1[,-17],x=bundles,z=levelnames)
```
conjoint analysis for cluster 2
```{r}
cluster2 <- clusters[clusters[,"segment"] == 2,] # respondents in cluster 2
#Conjoint(y=cluster2[,-17],x=bundles,z=levelnames)
```
Visualization of the division into 2 segments
```{r}
dcf<-discrcoord(segments$util,segments$sclu) 
assignments<-augment(segments$segm,dcf$proj[,1:2]) 
ggplot(assignments)+geom_point(aes(x=X1,y=X2,color= .cluster),size =4)+
  theme(panel.background = element_rect(fill="white"),axis.line = element_line(size=0.3,colour="black"),
        axis.text.x = element_text(size=10,colour="black"),
        axis.text.y = element_text(size=10,colour="black"))+
  labs(color="Cluster Assignment",title="K-Means Clustering Results")
```

## Market share analysis
Function to calculate market share percentage
```{r}
Market_share <- function(partworths,simulations) {
  # partworths could be the output from caPartUtilities()
  # simulations is bundles description (not coded version) with attribute name as the first column 
  for (j in seq(1:length(colnames(simulations)))) {
    mylist<- c()
    for (i in seq(1:length(colnames(partworths)))) {
      coln <- colnames(partworths)[i]
      if (coln %in% simulations[,j] || coln == "intercept"){
        mylist<- c(mylist,coln)
        pat <- quo_name(enquo(j))
        newN <- paste0(pat, "_sum")
        newPref <-partworths %>%
          select(all_of(mylist)) %>% 
          reduce(`+`) 
        partworths<-partworths %>%
          mutate(!!newN := newPref)
      }
    }
  }
  new_preferances<-partworths[,17:ncol(partworths)]
  projected_purchase <-colnames(new_preferances)[apply(new_preferances, 1,which.max)]
  Purchase <-data.frame(table(projected_purchase))
  Purchase$projected_purchase <-colnames(simulations)
  Purchase <- Purchase %>% mutate(Purchase, share_percentage = (Purchase$Freq)*100/ sum(Purchase$Freq))
  Purchase$projected_purchase <- factor(Purchase$projected_purchase, levels = Purchase$projected_purchase)
  return(Purchase)
}
```
Market_share of Bundle09 when launched with existing profiles
```{r, fig.width=5,fig.height=2}
partworth_each <-as.data.frame(part_utilities) # partworths of each respondent : can use given values as well
simulation1<- cbind(existing_prof_data, bundles_data$Bundle09)[,-1]

existing_and_bundle9<-Market_share(partworth_each,simulation1)
existing_and_bundle9
#write.csv(existing_and_bundle9, "existing_and_bundle9_market_shares.csv")
p1<-ggplot(existing_and_bundle9, aes(x=projected_purchase,y=share_percentage,fill=projected_purchase)) + geom_bar(stat="identity")
p1<-p1+scale_fill_manual(values=c( "#b2df8a", "#b2df8a", "#b2df8a","#b2df8a","#b2df8a","#1f78b4"))
p1
```
Market_share of Bundle09 when launched with new profiles
```{r,fig.width=5,fig.height=2}
partworth_each <-as.data.frame(part_utilities) # partworths of each respondent : can use given values as well
simulation2<- cbind(new_prof_data, bundles_data$Bundle09)[,-1]

new_and_bundle9<-Market_share(partworth_each,simulation2)
new_and_bundle9
#write.csv(new_and_bundle9, "new_and_bundle9_market_shares.csv")
p2<-ggplot(new_and_bundle9, aes(x=projected_purchase,y=share_percentage,fill=projected_purchase)) + geom_bar(stat="identity")
p2<-p2+scale_fill_manual(values=c( "#b2df8a", "#b2df8a", "#b2df8a","#b2df8a","#1f78b4"))
p2
```




